Evaluating isolation and contact tracing to control pandemic potential influenza outbreaks

### 2025-05-15 inst/paper/main.tex
add results and plots for median_controlled_outbreak_size and prop_controlled_outbreak

@@

>>>>

The median size of contained influenza outbreaks is predominantly below 100 cases for all influenza subtypes and isolation response delays (Figure \ref{fig:median-controlled-outbreak-size}). There are a few parameter sets that have a median cumulative outbreak size between 200 --- 400, but very few have 400 --- 500. This elucidates that when an outbreak is eliminated by isolation alone or in combination with contact tracing across ascertainment levels, it is done so with a relatively small number of cases (Figure \ref{fig:median-controlled-outbreak-size}). The total size of controlled outbreaks is also relatively constant across influenza subtypes and isolation response (Figure \ref{fig:median-controlled-outbreak-size}), noting that that the percentage of controlled outbreaks between parameter sets varies drastically with some only producing uncontrolled outbreaks (Figure \ref{fig:prop-controlled-outbreak}, \ref{fig:prop-outbreak-control-R}). \\

\begin{figure}[ht]
\centering
\includegraphics[width=\textwidth]{../plots/median_controlled_outbreak_size.png}
\caption{Median...}
\label{fig:median-controlled-outbreak-size}
\end{figure}

@@

\begin{figure}[ht]
\centering
\includegraphics[width=\textwidth]{../plots/prop_controlled_outbreak.png}
\caption{Median...}
\label{fig:prop-controlled-outbreak}
\end{figure}
